Co-methylation review

### 2015-05-07 Rmarkdown/comethylation.Rmd
Fix printing related glitches

The results of each simulation are summarised by a plot of $\widehat{\theta}_{0.5}$ (histogram), the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange), and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The density of $\theta_{k}$, the value of the true log odds ratio in the $k^{th}$ slice of the $2 \times 2 \times K$ table, is shown by a dashed black line[^density].

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_1.pdf}
\caption[Simulation 1a]{Results of simulation 1a ($K = 100$). Estimating the log odds ratio, $\theta = 0$ (shown by the dashed line), from a $2 \times 2 \times 100$ contingency table when the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are equal. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_1a}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_2.pdf}
\caption[Simulation 1b]{Results of simulation 1b ($K = 1000$). Estimating the log odds ratio, $\theta = 0$ (shown by the dashed line), from a $2 \times 2 \times 1000$ contingency table when the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are equal. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_1b}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_2d.pdf}
\caption[Simulation 1c]{Results of simulation 1c ($K = 1000$). Estimating the log odds ratio, $\theta = 0$ (shown by the dashed line), from a $2 \times 2 \times 1000$ contingency table when the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are equal. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $10,000$.}
\label{fig:Simulation_1c}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_3.pdf}
\caption[Simulation 2]{Results of simulation 2 ($K = 100$). Estimating the log odds ratio, $\theta$ (shown by the dashed line), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Uniform(0, 1)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_2}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_4.pdf}
\caption[Simulation 3]{Results of simulation 3 ($K = 100$). Estimating the log odds ratio, $\theta$ (shown by the dashed line), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_3}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_5.pdf}
\caption[Simulation 4a]{Results of simulation 4a ($K = 100$). Estimating a heterogeneous log odds ratio, $\theta_{k} = Gaussian(\theta_{0}, 1)$ (density shown by the dashed line), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_4a}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_6.pdf}
\caption[Simulation 4b]{Results of simulation 4b ($K = 1000$). Estimating a heterogeneous log odds ratio, $\theta_{k} = Gaussian(\theta_{0}, 1)$ (density shown by the dashed line), from a $2 \times 2 \times 1000$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_4b}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_7.pdf}
\caption[Simulation 5]{Results of simulation 5 ($K = 100$). Estimating a heterogeneous log odds ratio, $\theta_{k} = Skewed\text{-}Gaussian(\theta_{0}, 1, -10)$ (density shown by the dashed line), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_5}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_8.pdf}
\caption[Simulation 6]{Results of simulation 5 ($K = 100$). Estimating a heterogeneous log odds ratio, $\theta_{k} = 0.5 \times Gaussian(- \theta_{0}, 1) + 0.5 \times Gaussian(\theta_{0}, 1)$ (density shown by the dashed line), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (solid line) and $95 \%$ confidence interval (dashed lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_6}
\end{figure}

>>>>

The results of each simulation are summarised by a plot of $\widehat{\theta}_{0.5}$ (histogram), the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange), and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The density of $\theta_{k}$, the value of the true log odds ratio in the $k^{th}$ slice of the $2 \times 2 \times K$ table, is shown by a black curve[^density].

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_1.pdf}
\caption[Simulation 1a]{Results of simulation 1a ($K = 100$). Estimating the log odds ratio, $\theta = 0$ (shown by the black line), from a $2 \times 2 \times 100$ contingency table when the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are equal. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_1a}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_2.pdf}
\caption[Simulation 1b]{Results of simulation 1b ($K = 1000$). Estimating the log odds ratio, $\theta = 0$ (shown by the black line), from a $2 \times 2 \times 1000$ contingency table when the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are equal. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_1b}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_2d.pdf}
\caption[Simulation 1c]{Results of simulation 1c ($K = 1000$). Estimating the log odds ratio, $\theta = 0$ (shown by the black line), from a $2 \times 2 \times 1000$ contingency table when the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are equal. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $10,000$.}
\label{fig:Simulation_1c}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_3.pdf}
\caption[Simulation 2]{Results of simulation 2 ($K = 100$). Estimating the log odds ratio, $\theta$ (shown by the black line, $-4, -3, \ldots, 3, 4$ across the panels), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Uniform(0, 1)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_2}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_4.pdf}
\caption[Simulation 3]{Results of simulation 3 ($K = 100$). Estimating the log odds ratio, $\theta$ (shown by the black line, $-4, -3, \ldots, 3, 4$ across the panels), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_3}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_5.pdf}
\caption[Simulation 4a]{Results of simulation 4a ($K = 100$). Estimating a heterogeneous log odds ratio, $\theta_{k} = Gaussian(\theta_{0}, 1)$ (density shown by the black curve), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_4a}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_6.pdf}
\caption[Simulation 4b]{Results of simulation 4b ($K = 1000$). Estimating a heterogeneous log odds ratio, $\theta_{k} = Gaussian(\theta_{0}, 1)$ (density shown by the black curve), from a $2 \times 2 \times 1000$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_4b}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_7.pdf}
\caption[Simulation 5]{Results of simulation 5 ($K = 100$). Estimating a heterogeneous log odds ratio, $\theta_{k} = Skewed\text{-}Gaussian(\theta_{0}, 1, -10)$ (density shown by the black curve), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_5}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../figures/Simulation_8.pdf}
\caption[Simulation 6]{Results of simulation 5 ($K = 100$). Estimating a heterogeneous log odds ratio, $\theta_{k} = 0.5 \times Gaussian(- \theta_{0}, 1) + 0.5 \times Gaussian(\theta_{0}, 1)$ (density shown by the black curve), from a $2 \times 2 \times 100$ contingency table where the marginal probabilities, $\pi_{2+}$ and $\pi_{+2}$, are distributed as $Beta(0.3, 0.2)$ random variables. The results of three estimators of $\theta$ are shown: $\widehat{\theta}_{0.5}$ (histogram); the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{U}$ (coloured orange); and the point estimate (inner line) and $95 \%$ confidence interval (outer lines) of $\widehat{\theta}_{MH}$ (coloured blue). The average sample size (sequencing-coverage) of each $2 \times 2$ table is $30$.}
\label{fig:Simulation_6}
\end{figure}

### 2015-05-07 Rmarkdown/comethylation_review.Rmd
Fix printing related glitches

\begin{figure}[!htb]
\centering
\includegraphics[width=0.8\textwidth]{../figures/Lister_2009_Sup_Fig_9.pdf}
\caption[Co-methylation figure from \citet{Lister:2009hy}]{Spacing of Adjacent Methylcytosines in Different Contexts. Prevalence of mCHG/mCHH sites (y-axis) as a function of the number of bases between adjacent mCHG/mCHH sites (x-axis) based on all non redundant pair-wise distances up to $50$ nt in exons, introns and random sequences. The blue line represents smoothing by cubic splines. Adapted by permission from from Macmillan Publishers Ltd: [Nature Genetics] (\citet{Lister:2009hy}), copyright (2009)}
\label{fig:Lister_2009_Sup_Fig_9}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.8\textwidth]{../figures/Cokus_2008_Sup_Fig_14.pdf}
\caption[Co-methylation figure from \citet{Cokus:2008fc}]{Within-read probability of additional methylation of CHH sites within a given distance from a methylated CHH site. Data were derived from individual BS-Seq reads. The x-axis indicates the distance between the two cytosines. The y-axis indicates the probability of methylation of CHH sites within the given distance from another methylated CHH site. Each point is the mean value from averaging the probability from each of the five Arabidopsis chromosomes, and the blue line is a running average of these mean values. Error bars represent $95\%$ confidence intervals via critical values of Student $t$ distributions. Adapted by permission from from Macmillan Publishers Ltd: [Nature Genetics] (\citet{Cokus:2008fc}), copyright (2008).}
\label{fig:Cokus_2008_Sup_Fig_14}
\end{figure}

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=0.8\textwidth]{../figures/Lister_2009_Sup_Fig_9.jpg}
\caption[Co-methylation figure from \citet{Lister:2009hy}]{Spacing of Adjacent Methylcytosines in Different Contexts. Prevalence of mCHG/mCHH sites (y-axis) as a function of the number of bases between adjacent mCHG/mCHH sites (x-axis) based on all non redundant pair-wise distances up to $50$ nt in exons, introns and random sequences. The blue line represents smoothing by cubic splines. Adapted by permission from from Macmillan Publishers Ltd: [Nature Genetics] (\citet{Lister:2009hy}), copyright (2009)}
\label{fig:Lister_2009_Sup_Fig_9}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.8\textwidth]{../figures/Cokus_2008_Sup_Fig_14.jpg}
\caption[Co-methylation figure from \citet{Cokus:2008fc}]{Within-read probability of additional methylation of CHH sites within a given distance from a methylated CHH site. Data were derived from individual BS-Seq reads. The x-axis indicates the distance between the two cytosines. The y-axis indicates the probability of methylation of CHH sites within the given distance from another methylated CHH site. Each point is the mean value from averaging the probability from each of the five Arabidopsis chromosomes, and the blue line is a running average of these mean values. Error bars represent $95\%$ confidence intervals via critical values of Student $t$ distributions. Adapted by permission from from Macmillan Publishers Ltd: [Nature Genetics] (\citet{Cokus:2008fc}), copyright (2008).}
\label{fig:Cokus_2008_Sup_Fig_14}
\end{figure}
